---
title: "realpage analysis"
author: "Mason Gatewood"
date: '2023-01-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Load in Tidyverse for data analysis, zipcodeR to join to the Builtwith data, sf and spData for spatial analysis

```{r}
library(tidyverse)
library(zipcodeR)
library(sf)
library(spData)
```

Read in Builtwith data on Realpage and select relevant fields

```{r}
real_page <- read.csv("rp-data.CSV")

real_page <- real_page %>%  select(Domain, Telephones, Emails, Twitter, Facebook, LinkedIn, Google, Pinterest, GitHub, Instagram, Vk, Vimeo, Youtube, TikTok, People, City, State, Zip, Country, Last.Indexed)

glimpse(real_page)
```

Join Realpage data with zipcode information from zipcodeR

```{r}
joined_data <- real_page %>% left_join(zip_code_db, by=c('Zip' = 'zipcode'))
glimpse(joined_data)
```

First plot of companies potentially using Realpage products grouped by zipcode

```{r}
joined_data %>% 
  group_by(Zip, major_city, state, lat, lng) %>% 
  summarize(count = n()) %>% 
  drop_na(major_city) %>% 
  ggplot(aes(x = lng, y = lat, size = count)) +
  geom_point() +
  borders("state") +
  theme_void()
```

Convert long and lat to geometric point

```{r}
joined_data <- joined_data %>% 
  drop_na(lat, lng) %>% 
  mutate(lat = as.numeric(lat),
         lng = as.numeric(lng)) %>% 
  st_as_sf(coords = c("lng", "lat"))

glimpse(joined_data)
```

Import shapefile of all zipcodes in United States

```{r}
zip_shape <- read_sf("~/Desktop/zipshape")

glimpse(zip_shape)
```

Only select zipcodes that interesect with points in joined_data

